### 2019-09-15 reports/thesis/chapters/5_inference.tex
Revise

Disagreement between the obtained and the \emph{aRTist} simulated projections can be found by subtracting one projection from the other, any values too big in magnitude can be considered as a defect. However in the previous chapters, it was found that x-ray photons behave randomly and differences in the comparison can be due to chance. Thus the comparisons should be done under the face of uncertainty.

A pixel by pixel inference was proposed to do defect detection. A test statistic $Z_{x,y}$ was calculated for all pixels at $(x,y)$. This test statistic is
\begin{equation}
  Z_{x,y} = 
  \dfrac{
    \text{projection}_{x,y} - \emph{aRTist}_{x,y}
  }
  {
    \sqrt{\widehat{\variance}\left[\text{projection}_{x,y}\right]}
  }
\end{equation}
where $\widehat{\variance}\left[\text{projection}_{x,y}\right]$ is the estimated grey value variance of pixel $(x,y)$ in the projection. For high photon rate, it was shown in the previous chapters that the grey values in the scan can be modelled using a Normal distribution. Thus by treating the simulated projection from \emph{aRTist} as known and the ground truth, then the randomness of the test statistics, assuming there are no defects, can be approximately quantified as
\begin{equation}
Z_{x,y}\sim \normal(0,1) \ .
\end{equation}
As with usual statistical convention, upper case $Z$ denote a random variable. Lower case $z$ denote a realisation or an observation of that random variable.

To illustrate this method of inference, the projections from the dataset \texttt{AbsFilter} at \ang{120} was used. To recap, replicate projections of a test sample with purposefully manufactured voids were obtained. \emph{aRTist} was used to create a simulation of that projection but as if the voids were not there. Thus the method should pick these voids up.

A projection and the \emph{aRTist} projection is shown in Figures \ref{fig:inference_inferenceIntro_inference_scan} and \ref{fig:inference_inferenceIntro_inference_artist} respectively. The 20 replicate projections were spilt into two. 19 randomly selected projections were used for the variance-mean model to fit onto. A gamma GLM with a basic linear relationship was used. The remaining projection was compared with the \emph{aRTist} projection, the variance was predicted using the grey value in the \emph{aRTist} simulation as the predictor variable.

\begin{figure}
  \centering
  \centerline{
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/inference/inferenceIntro_scan.eps}
      \caption{X-ray image}
      \label{fig:inference_inferenceIntro_inference_scan}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/inference/inferenceIntro_artist.eps}
      \caption{\texttt{aRTist} simulation}
      \label{fig:inference_inferenceIntro_inference_artist}
    \end{subfigure}
  }
  \centerline{
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/inference/inferenceIntro_logp.eps}
      \caption{$-\log p\text{-values}$}
      \label{fig:inference_inferenceIntro_inference_pvalue}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/inference/inferenceIntro_positivePixels.eps}
      \caption{Positive pixels}
      \label{fig:inference_inferenceIntro_inference_positivePixels}
    \end{subfigure}
  }
  \caption{A projection of the test sample, from the \texttt{AbsFilter} at \ang{120} dataset, was compared to the \emph{aRTist} simulated projection to detect the purposefully manufactured voids. The $p$-values obtained were used for hypothesis testing, using the \cite{benjamini1995controlling} procedure, at the 5\% FDR level. Pixels detected as positive are shown in red in d).}
  \label{fig:inference_inferenceIntro_inference}
\end{figure}

For each pixel, a test statistic was calculated. A test statistic too large in magnitude, relative to the anticipated variance, will classify that pixel as a positive result. In two-tailed hypothesis testing \citep{pearson1900on, neyman1933on, fisher1970statistical}, the $p$-value can be used to represent test statistic in a different way
\begin{equation}
  p_{x,y} = 2(1-\Phi(|z_{x,y}|))
\end{equation}
which can takes values $0\leqslant p_{x,y} \leqslant 1$. A $p$-value too small is considered a positive result. The $p$-values are shown in Figure \ref{fig:inference_inferenceIntro_inference_pvalue}.

The resulting $p$-values are concerning. This is because the $p$-values are not very smooth on the surfaces of the sample. It should be expected that small $p$-values are in areas of the defects. Pixels are tested positive, or considered to be evidence of a defect, when $|z_{x,y}|>\inputNumber{../figures/inference/inferenceIntro_critical.txt}$. This value was chosen by controlling the false discovery rate at 5\% using the \cite{benjamini1995controlling} (BH) procedure. The positive pixels are shown in Figure \ref{fig:inference_inferenceIntro_inference_positivePixels}.

@@

Model misspecification appeared to be the main source of error. The test statistics and $p$-values were inspected in Figure \ref{fig:inference_inferenceIntro_histogram}. It can be seen that the majority of the test statistics does come from a Normal distribution. Also, the majority of the $p$-values are not look uniformly distributed. This seems to suggest that the assumption of $Z_{x,y}\sim \normal(0,1)$ is incorrect.

\begin{figure}
  \centering
  \centerline{
  \begin{subfigure}[b]{\subSize}
    \includegraphics[width=\textwidth]{../figures/inference/inferenceIntro_histogram.eps}
    \caption{Histogram}
  \end{subfigure}
  \begin{subfigure}[b]{\subSize}
    \includegraphics[width=\textwidth]{../figures/inference/inferenceIntro_pValue.eps}
    \caption{$p$-values}
    \label{fig:inference_inferenceIntro_pvalue}
  \end{subfigure}
}
  \caption{a) The histogram of the test statistics is compared with the standard Normal distribution. The standard Normal distribution is known as the null distribution in this scenario. b) The $p$-values are ordered and plotted. The critical region corresponds to controlling the false discovery rate at 5\% using the \cite{benjamini1995controlling} procedure. The dotted line shows the result if the $p$-values were uniformly distributed.}
  \label{fig:inference_inferenceIntro_histogram}
\end{figure}

@@

Consider a test statistic from a pixel. If there are no defects, then the statistic is null and has the null distribution $Z|H_0\sim\normal(0,1)$. This can be described in another way by specifying the random variable as $Z\sim\normal(\mu,1)$ and the null hypothesis as $H_0:\mu=0$. A hypothesis test can judge how much $Z$ deviates from 0 by defining the alternative hypothesis $H_1:\mu\neq 0$. A statistic which does not have the null distribution is known as non-null.

In two-tailed hypothesis testing \citep{pearson1900on, neyman1933on, fisher1970statistical}, the $p$-value can be compared with the user defined significance level $\alpha$, also known as the size of the test in this specific example. A positive result is declared when $p<\alpha$, else it is a negative result. Correct and incorrect testing of the statistics can occur. For example testing a null statistic as positive is known as a false positive. It can be shown that $\alpha$ controls the false positive rate. $\alpha=5.0\%$ is a typical choice \citep{wasserstein2019moving} and is used throughout this thesis. Other fields use the $\sigma$ notation, for example $2\sigma$ correspond to about the $\alpha = 4.6\%$ significance level; this notation will not be used here.

Multiple hypothesis testing occurs when there are more than one hypotheses to test. For example $n$ pixels can be tested where the test statistics are $Z_1, Z_2, \dotsc, Z_n$ and $Z_i\sim\normal(\mu_i,1)$ for $i=1,2,\dotsc,n$. The null hypotheses are $H_{0,i}:\mu_i=0$ and are tested against the alternative $H_{1,i}:\mu_i\neq 0$ for $i=1,2,\dotsc,n$. Let the corresponding $p$-values be $p_1, p_2, \dotsc, p_n$.

The uncorrected test classify any $p_i<\alpha$ as positive. This is flawed because the possibility of obtaining at least one false positive increases as the number of tests increases \citep{shaffer1995multiple}. This method does control the per comparison error rate (PCER) \citep{benjamini1995controlling}. PCER is the proportion of false positives out of all tests. The number of true/false positive/negatives obtained are defined in Table \ref{table:inference_randomvariables}. Using the notation, PCER is defined as
\begin{equation}
  \text{PCER}=
  \dfrac{1}{n}
  \expectation[V]
  \ .
\end{equation}
It can be seen that if the uncorrected test controls the false positive rate such that $\expectation[V]/n_0 = \alpha$, then it controls the PCER such that
\begin{equation}
  \text{PCER}\leqslant\alpha \ .
\end{equation}

\begin{table}
  \centering
  \begin{tabular}{c|c|c|c}
    &Negative&Positive&Total\\\hline
    Null & $U$ & $V$ & $n_0$\\
    Non-null & $T$ & $S$ & $n-n_0$\\\hline
    &$n-R$&$R$&$n$
  \end{tabular}
  \caption{Random variable definitions for the number of true/false positives/negatives made in multiple hypothesis testing}
  \label{table:inference_randomvariables}
\end{table}

The Bonferroni correction \citep{shaffer1995multiple, bland1995multiple, perneger1998what} controls the family-wise error rate (FWER) \citep{shaffer1995multiple} where
\begin{equation}
  \text{FWER} = \prob(V\geqslant1) \ .
  \label{eq:inference_fwer}
\end{equation}
This is done by adjusting the size of the test to be $\alpha/n$. By using the adjusted size, then $\text{FWER}=1-\left[(1-\alpha/n)^n\right]$. Using the approximation $(1-\alpha/n)^n\approx 1-\alpha$ then $\text{FWER}\approx \alpha$. This shows that the Bonferroni correction controls the family-wise error rate such that
\begin{equation}
  \text{FWER} \leqslant \alpha \ .
\end{equation}
However, in practice the Bonferroni correction is not very powerful \citep{perneger1998what}, meaning it gives too many false negatives. This is because the correction traded too many false positives for false negatives.

@@

The BH procedure adjust the size of the test between the Bonferroni correction and the uncorrected test. It adapts to the data and choose different sizes for different data. The procedure is as follows, the $p$-values are ordered such that $p_{(1)}\leqslant p_{(2)}\leqslant \dotsc \leqslant p_{(n)}$. Suppose a size $\alpha$ is provided beforehand. The size is adjusted to
\begin{equation}
  \alpha_{\text{BH}} = \frac{\alpha k}{n}
\end{equation}
where
\begin{equation}
  k\text{ is the largest }i\text{ for which }p_{(i)}\leqslant\frac{i}{n}\alpha
  \ .
\end{equation}
This test the statistics with $p$-values $p_{(1)},p_{(2)},\dotsc,p_{(k)}$ as positive. For the case where $p_{(1)}>\alpha/n$ then $k=1$ so that the Bonferroni correction is used when there are no positive results, this is only for illustration purposes. For example in Figure \ref{fig:inference_inferenceIntro_pvalue}, the $p$-values were plotted against their order so that the critical boundary was shown by a linear curve with gradient $\alpha/n$.

The BH procedure comes from the fact that if all the statistics are null and independent, then the $p$-values are uniformly distributed \citep{simes1986improved}. However it can be shown that the BH procedure works for many scenarios of dependencies \citep{benjamini2001control}. It can be shown that the BH procedure controls the FDR such that
\begin{equation}
  \text{FDR}\leqslant\alpha
\end{equation}
\citep{benjamini1995controlling}.

@@

\begin{table}
    \centering
    \begin{tabular}{c|c}
        Correction&Controls for\\\hline
        No correction&$\text{PCER}\leqslant\alpha$\\
        Bonferroni&$\text{FWER}\leqslant\alpha$\\
        BH&$\text{FDR}\leqslant\alpha$
    \end{tabular}
    \caption{Different types of corrections for multiple hypothesis testing are listed here, along with what they control for.}
    \label{table:inference_corrections}
\end{table}

Consider a small example where a $200\times200$ section of the $z$ image was investigated, as shown Figure \ref{fig:inference_inferenceSubsample1_histogram}. The distribution of the test statistics appeared Normal but not centred at zero. So by using the BH procedure to obtain a critical region of $|Z|>\input{../figures/inference/inferenceSubsample1_criticalBoundary.txt}$, almost half of the pixels were tested positive. It is questionable whether such a number of positive results is sensible, in particular in an area where defects were not expected.

\begin{figure}
  \centering
    \centerline{
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/inference/inferenceSubsample1_zImage.eps}
      \caption{Test statistics}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/inference/inferenceSubsample1_histogram.eps}
      \caption{Histogram of test in sub-image}
    \end{subfigure}
    }
    \caption{The resulting $z$ image is shown in a). A $200\times 200$ sub-image was taken shown by the dashed lines. A histogram of the test statistics in the sub-image is shown in b). The critical region was obtained by using the BH procedure at the 5\% FDR level.}
    \label{fig:inference_inferenceSubsample1_histogram}
\end{figure}

This problem commonly occur in large scale multiple hypothesis testing \citep{efron2004large} such as in microarrays \citep{hedenfalk2001gene, efron2002empirical, efron2003robbins}. It appears that the null distribution was misspecified as $Z_i|H_{0,i}\sim\normal(0,1)$ when in reality they are distributed as $Z_i|H_{0,i}\sim\normal(\mu_0,\sigma_0^2)$, where $\mu_0$ and $\sigma_0$ are the null mean and null standard deviation respectively.

@@

In \cite{efron2004large}, a few assumptions were made in order to obtain the estimators $\widehat{\mu}_0$ and $\widehat{\sigma}_0$. Let the test statistic $Z$ have the p.d.f.
\begin{equation}
  p_Z(z) =
  \pi_0 p_{Z|H_0}(z) + \pi_1 p_{Z|H_1}(z)
\end{equation}
where $0\leqslant\pi_0\leqslant 1$ and  $\pi_1 = 1-\pi_0$. In addition, the null distribution is
\begin{equation}
  p_{Z|H_0}(z) = 
  \dfrac{1}{\sqrt{2\pi}\sigma_0}
  \exp\left[
    -\dfrac{1}{2}
    \left(
      \dfrac{z-{\mu}_0}{\sigma_0}
    \right)^2
  \right]
\end{equation}
as it was assumed to be Normal. The non-null distribution $p_{Z|H_1}(z)$ does not need to be specified. Assume that the majority of the data are null and non-null test statistics are rare, say $\pi_0>0.9$ \citep{efron2004large}. Then around the mode, the probability density function would be dominated by the null distribution. This implies that
\begin{equation}
  p_{Z}(z) \approx \pi_0 p_{Z|H_0}(z)
\end{equation}
for values of $z$ around the mode. Finding the mode for $p_{Z}(z)$ and $p_{Z|H_0}(z)$ should yield the same solution. This justify the use of the mode for the empirical null mean \citep{efron2004large}
\begin{equation}
  \widehat{\mu}_0 = \argmax\widehat{p}_Z(z)
\end{equation}
where $\widehat{p}_Z(z)$ is the density estimation of $p_Z(z)$, for example it could be a smoothing spline fitted onto the histogram \citep{efron2004large}.

The null standard deviation is estimated from the log density \citep{efron2004large}. For values of $z$ at and around the mode
\begin{equation}
  \ln p_{Z}(z) = 
  \ln\left[
    \dfrac{\pi_0}{\sqrt{2\pi}{\sigma}_0}
  \right]
  -\dfrac{1}{2}
  \left(
    \dfrac{z-{\mu}_0}{{\sigma}_0}
  \right)^2
  \ .
\end{equation}
Taking derivatives
\begin{align}
  \dfrac{\partial}{\partial z} \ln p_{Z}(z) &=
  -\left(
    \dfrac{
      z-{\mu}_0
    }
    {
      {\sigma}_0^2
    }
  \right)
  \nonumber\\
  &=
  -\dfrac{
    1
  }
  {
    {\sigma}_0^2
  }
\end{align}
which motivates the estimator \citep{efron2004large}
\begin{equation}
  \widehat{\sigma}_0 = \left[
    \left.
      -\dfrac{\partial^2}{\partial z^2}\ln\widehat{p}(z)
    \right|_{z=\widehat{\mu}_0}
  \right]^{-1/2}
  \ .
  \label{eq:inference_nullStdEstimator}
\end{equation}
The evaluation of $z=\widehat{\mu}_0$ is used because at the mode, it was assumed that the null test statistics would dominate and non-null test statistics would not contribute much to the density estimate.

This method does not need estimations of $\pi_0$ which makes it quite convenient. The estimations of $\pi_0$ is discussed in literature such as \cite{benjamini2000adaptive, pounds2003estimating, storey2003statistical, pounds2004improving, langaas2005estimating, durnez2014posthoc}. \cite{efron2004large} motives the use of the empirical null by investigating various types of false discovery rates \citep{storey2002direct, storey2003positive, efron2002empirical, efron2007size} which will not be discussed here.

The empirical null is used widely, including in neuroimaging \citep{schwartzman2008false, schwartzman2009empirical} and has been extended to include non-Normal null distributions \citep{schwartzman2008false, schwartzman2008empirical}. There exist various methods for the empicial null. \cite{schwartzman2008empirical} used Poisson regression on the histogram counts in regions where the null statistics dominate. The empirical characteristic function was used in \cite{jin2007estimating}.

@@

The null mean was estimated by numerically finding the mode of the density estimate. The null standard deviation was estimated using Equation \eqref{eq:inference_nullStdEstimator}. This results in the empirical null density to have the same curvature as the density estimate at the mode, this is illustrated in Figure \ref{fig:inference_inferenceSubsample1_densityEstimate}. In this particular example, it was found that $\widehat{\mu}_0=\input{../figures/inference/inferenceSubsample1_nullMean.txt}$ and $\widehat{\sigma}_0=\input{../figures/inference/inferenceSubsample1_nullStd.txt}$ to 2 decimal places.

@@

The mode was found by solving $\widehat{\mu}_0 = \argmax\widehat{p}_Z(z)$ numerically. The Newton-Raphson method was used to solve

@@

  \right) $
so that the log density is

@@

Taking the first derivative

>>>>

Disagreement between the obtained and the \emph{aRTist} simulated projections can be found by subtracting one projection from the other. Any values too big in magnitude can be considered as a defect. However, in the previous chapters, it was found that x-ray photons behave randomly and differences in the comparison can be due to chance. Thus, the comparisons should be done in the face of uncertainty.

A pixel by pixel hypothesis test was proposed to do defect detection. The test statistic, for the pixel located at $(x,y)$, is
\begin{equation}
  Z_{x,y} = 
  \dfrac{
    \text{projection}_{x,y} - \emph{aRTist}_{x,y}
  }
  {
    \sqrt{\widehat{\variance}\left[\text{projection}_{x,y}\right]}
  }
\end{equation}
where $\widehat{\variance}\left[\text{projection}_{x,y}\right]$ is the estimated grey value variance. The test statistic was calculated for each pixel in the projection. For high photon rate, it was shown in the previous chapters that the grey values in the scan can be modelled using a Normal distribution. Thus, if there are no significant differences between the obtained and \emph{aRTist} projections, then the randomness of the test statistics can be approximately quantified as
\begin{equation}
Z_{x,y}\sim \normal(0,1) \ .
\end{equation}
As with usual statistical convention, an upper case $Z$ denotes a random variable. A lower case $z$ denotes a realisation or an observation of that random variable.

To illustrate this method of inference, the projections from the dataset \texttt{AbsFilter} at \ang{120} was used. To recap, replicate projections of a test sample, with purposefully manufactured voids, were obtained. \emph{aRTist} was used to create a simulation of that projection but as if the voids were not there. Thus the method should pick these voids up.

The obtained and \emph{aRTist} projections are shown in Figures \ref{fig:inference_inferenceIntro_inference_scan} and \ref{fig:inference_inferenceIntro_inference_artist} respectively. The 20 replicate projections were spilt into two. 19 randomly selected projections were used for the variance-mean model to fit onto. A gamma GLM, with a basic linear relationship, was used for the variance-mean model. The remaining projection was compared with the \emph{aRTist} projection. The variance was predicted using the grey value in the \emph{aRTist} simulation as the predictor variable.

\begin{figure}
  \centering
  \centerline{
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/inference/inferenceIntro_scan.eps}
      \caption{X-ray image}
      \label{fig:inference_inferenceIntro_inference_scan}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/inference/inferenceIntro_artist.eps}
      \caption{\texttt{aRTist} simulation}
      \label{fig:inference_inferenceIntro_inference_artist}
    \end{subfigure}
  }
  \centerline{
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/inference/inferenceIntro_logp.eps}
      \caption{$-\log p\text{-values}$}
      \label{fig:inference_inferenceIntro_inference_pvalue}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/inference/inferenceIntro_positivePixels.eps}
      \caption{Positive pixels}
      \label{fig:inference_inferenceIntro_inference_positivePixels}
    \end{subfigure}
  }
  \caption{A projection of the test sample, from the \texttt{AbsFilter} at \ang{120} dataset, was compared to the \emph{aRTist} simulated projection to detect purposefully manufactured voids. The $p$-values obtained were used for hypotheses testing. Pixels detected as positive are shown in red in d) using the \cite{benjamini1995controlling} procedure at the 5\% false discovery rate level.}
  \label{fig:inference_inferenceIntro_inference}
\end{figure}

For each pixel, a test statistic was calculated, which forms a $z$ image. A test statistic too large in magnitude, relative to the anticipated variance, will classify that pixel as a positive result. In two-tailed hypothesis testing \citep{pearson1900on, neyman1933on, fisher1970statistical}, $p$-values can be used to represent the test statistics in a different way
\begin{equation}
  p_{x,y} = 2(1-\Phi(|z_{x,y}|))
\end{equation}
which can takes values $0\leqslant p_{x,y} \leqslant 1$. A $p$-value too small is considered a positive result. The $p$-values are shown in Figure \ref{fig:inference_inferenceIntro_inference_pvalue}.

The resulting $p$-values are concerning. This is because the $p$-values are not very smooth on the surfaces of the sample. It should be expected that small $p$-values are in areas of the defects. Pixels were tested positive, or considered to be evidence of a defect, when $|z_{x,y}|>\inputNumber{../figures/inference/inferenceIntro_critical.txt}$ to 2 decimal places. This value was chosen by controlling the false discovery rate at 5\% using the \cite{benjamini1995controlling} (BH) procedure. The positive pixels are shown in Figure \ref{fig:inference_inferenceIntro_inference_positivePixels}.

@@

Model misspecification appeared to be the main source of error. The test statistics and $p$-values were inspected in Figure \ref{fig:inference_inferenceIntro_histogram}. It can be seen that the test statistics were not compatible with the standard Normal distribution. Also, the majority of the $p$-values did not look uniformly distributed. This seems to suggest that the assumption of $Z_{x,y}\sim \normal(0,1)$ is incorrect.

\begin{figure}
  \centering
  \centerline{
  \begin{subfigure}[b]{\subSize}
    \includegraphics[width=\textwidth]{../figures/inference/inferenceIntro_histogram.eps}
    \caption{Histogram}
  \end{subfigure}
  \begin{subfigure}[b]{\subSize}
    \includegraphics[width=\textwidth]{../figures/inference/inferenceIntro_pValue.eps}
    \caption{$p$-values}
    \label{fig:inference_inferenceIntro_pvalue}
  \end{subfigure}
}
  \caption{a) The histogram of the test statistics is compared with the standard Normal distribution. The standard Normal distribution is known as the null distribution in this scenario. b) The $p$-values are ordered and plotted. The critical region corresponds to controlling the false discovery rate at 5\% level using the \cite{benjamini1995controlling} procedure. The dotted line shows the result if the $p$-values were uniformly distributed.}
  \label{fig:inference_inferenceIntro_histogram}
\end{figure}

@@

Consider a test statistic $Z$ from a pixel. If there are no defects, then the statistic is null and has the null distribution $Z|H_0\sim\normal(0,1)$. This can be described by specifying the random variable as $Z\sim\normal(\mu,1)$ and the null hypothesis as $H_0:\mu=0$. A hypothesis test can judge how much $Z$ deviates from 0 by defining the alternative hypothesis $H_1:\mu\neq 0$. A statistic which does not has the null distribution is known as non-null.

In two-tailed hypothesis testing \citep{pearson1900on, neyman1933on, fisher1970statistical}, the $p$-value can be compared with the user-defined size of the test $\alpha$, also known as the significance level in this specific example. A positive result is declared when $p<\alpha$, else it is a negative result. Correct and incorrect testing of the statistics can occur. For example, testing a null statistic as positive is known as a false positive. It can be shown that $\alpha$ controls the false positive rate. $\alpha=5.0\%$ is a typical choice \citep{wasserstein2019moving} and is used throughout this thesis.

Multiple hypotheses testing occurs when there are more than one hypotheses to test. For example, $n$ pixels can be tested where the test statistics are $Z_1, Z_2, \dotsc, Z_n$ and $Z_i\sim\normal(\mu_i,1)$ for $i=1,2,\dotsc,n$. The null hypotheses are $H_{0,i}:\mu_i=0$ and are tested against the alternative $H_{1,i}:\mu_i\neq 0$ for $i=1,2,\dotsc,n$. Let the corresponding $p$-values be $p_1, p_2, \dotsc, p_n$.

The uncorrected test classify any $p_i<\alpha$ as positive. This is flawed because the possibility of obtaining at least one false positive increases as the number of tests increases \citep{shaffer1995multiple}. This method does control the per comparison error rate (PCER) \citep{benjamini1995controlling}. PCER is the proportion of false positives out of all tests. The notation for the number of true/false positive/negatives obtained are defined in Table \ref{table:inference_randomvariables}. Using the notation, the PCER is defined as
\begin{equation}
  \text{PCER}=
  \dfrac{1}{n}
  \expectation[V]
  \ .
\end{equation}
It can be seen that if the uncorrected test controls the false positive rate such that $\expectation[V]/n_0 = \alpha$, then it controls the PCER such that
\begin{equation}
  \text{PCER}\leqslant\alpha \ .
\end{equation}

\begin{table}
  \centering
  \begin{tabular}{c|c|c|c}
    &Negative&Positive&Total\\\hline
    Null & $U$ & $V$ & $n_0$\\
    Non-null & $T$ & $S$ & $n-n_0$\\\hline
    &$n-R$&$R$&$n$
  \end{tabular}
  \caption{Random variable definitions for the number of true/false positives/negatives made in multiple hypotheses testing}
  \label{table:inference_randomvariables}
\end{table}

The Bonferroni correction \citep{shaffer1995multiple, bland1995multiple, perneger1998what} controls the family-wise error rate (FWER) \citep{shaffer1995multiple} where
\begin{equation}
  \text{FWER} = \prob(V\geqslant1) \ .
  \label{eq:inference_fwer}
\end{equation}
This is done by adjusting the size of the test to be $\alpha/n$. By using the adjusted size, then $\text{FWER}=1-\left[(1-\alpha/n)^n\right]$. Using the approximation $(1-\alpha/n)^n\approx 1-\alpha$ then $\text{FWER}\approx \alpha$. This shows that the Bonferroni correction controls the family-wise error rate such that
\begin{equation}
  \text{FWER} \leqslant \alpha \ .
\end{equation}
In practice, the Bonferroni correction is not very powerful \citep{perneger1998what}, meaning it gives too many false negatives. This is because the correction traded too many false positives for false negatives.

@@

The BH procedure adjusts the size of the test between the Bonferroni correction and the uncorrected test. It adapts to the data and chooses different sizes for different data. The procedure is as follows, the $p$-values are ordered such that $p_{(1)}\leqslant p_{(2)}\leqslant \dotsc \leqslant p_{(n)}$. Suppose a size $\alpha$ is provided beforehand. The size is adjusted to
\begin{equation}
  \alpha_{\text{BH}} = \frac{\alpha k}{n}
\end{equation}
where
\begin{equation}
  k\text{ is the largest }i\text{ for which }p_{(i)}\leqslant\frac{i}{n}\alpha
  \ .
\end{equation}
This test the statistics with $p$-values $p_{(1)},p_{(2)},\dotsc,p_{(k)}$ as positive. For the case where $p_{(1)}>\alpha/n$ then $k=1$ so that the Bonferroni correction is used when there are no positive results, this is only for illustration purposes. For example in Figure \ref{fig:inference_inferenceIntro_pvalue}, the $p$-values were plotted against their order so that the critical boundary was shown by a linear curve with gradient $\alpha/n$.

The BH procedure comes from the fact that if all the statistics are null and independent, then the $p$-values are uniformly distributed \citep{simes1986improved}. However, it can be shown that the BH procedure works for many scenarios of dependencies \citep{benjamini2001control}. It can be shown that the BH procedure controls the FDR such that
\begin{equation}
  \text{FDR}\leqslant\alpha
\end{equation}
\citep{benjamini1995controlling}.

@@

\begin{table}
    \centering
    \begin{tabular}{c|c}
        Correction&Controls for\\\hline
        No correction&$\text{PCER}\leqslant\alpha$\\
        Bonferroni&$\text{FWER}\leqslant\alpha$\\
        BH&$\text{FDR}\leqslant\alpha$
    \end{tabular}
    \caption{Different types of corrections for multiple hypotheses testing are listed here, along with what they control for.}
    \label{table:inference_corrections}
\end{table}

Consider a small example where a $\SI{200}{\pixel}\times\SI{200}{\pixel}$ section of the $z$ image was investigated, as shown Figure \ref{fig:inference_inferenceSubsample1_histogram}. The distribution of the test statistics appeared Normal but not centred at zero. By using the BH procedure to obtain a critical region of $|Z|>\input{../figures/inference/inferenceSubsample1_criticalBoundary.txt}$ to 2 decimal places, almost half of the pixels were tested positive. It is questionable whether such a number of positive results is sensible, in particular, in an area where defects were not expected.

\begin{figure}
  \centering
    \centerline{
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/inference/inferenceSubsample1_zImage.eps}
      \caption{Test statistics}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/inference/inferenceSubsample1_histogram.eps}
      \caption{Histogram of test in sub-image}
    \end{subfigure}
    }
    \caption{The resulting $z$ image is shown in a). A $\SI{200}{\pixel}\times\SI{200}{\pixel}$ sub-image was taken shown by the dashed lines. A histogram of the test statistics in the sub-image is shown in b). The critical region corresponds to the 5\% FDR level.}
    \label{fig:inference_inferenceSubsample1_histogram}
\end{figure}

This problem commonly occurs in large scale multiple hypotheses testing \citep{efron2004large} such as in microarrays \citep{hedenfalk2001gene, efron2002empirical, efron2003robbins}. It appeared that the null distribution was misspecified as $Z_i|H_{0,i}\sim\normal(0,1)$ when in reality they are distributed as $Z_i|H_{0,i}\sim\normal(\mu_0,\sigma_0^2)$, where $\mu_0$ and $\sigma_0$ are the null mean and null standard deviation respectively.

@@

In \cite{efron2004large}, a few assumptions were made in order to obtain the estimators $\widehat{\mu}_0$ and $\widehat{\sigma}_0$. Let the test statistic $Z$ have the p.d.f.
\begin{equation}
  p_Z(z) =
  \pi_0 p_{Z|H_0}(z) + \pi_1 p_{Z|H_1}(z)
\end{equation}
where $0\leqslant\pi_0\leqslant 1$ and  $\pi_1 = 1-\pi_0$. In addition, the null distribution is
\begin{equation}
  p_{Z|H_0}(z) = 
  \dfrac{1}{\sqrt{2\pi}\sigma_0}
  \exp\left[
    -\dfrac{1}{2}
    \left(
      \dfrac{z-{\mu}_0}{\sigma_0}
    \right)^2
  \right]
\end{equation}
as it was assumed to be Normal. The non-null distribution $p_{Z|H_1}(z)$ does not need to be specified. Assume that the majority of the data are null and non-null test statistics are rare, say $\pi_0>0.9$ \citep{efron2004large}, then around the mode, the probability density function would be dominated by the null distribution. This implies that
\begin{equation}
  p_{Z}(z) \approx \pi_0 p_{Z|H_0}(z)
\end{equation}
for values of $z$ around the mode. Finding the mode for $p_{Z}(z)$ and $p_{Z|H_0}(z)$ should yield the same solution. This justify the use of the mode for the empirical null mean \citep{efron2004large}
\begin{equation}
  \widehat{\mu}_0 = \argmax\widehat{p}_Z(z)
\end{equation}
where $\widehat{p}_Z(z)$ is the density estimation of $p_Z(z)$, for example it could be a smoothing spline fitted onto the histogram \citep{efron2004large}.

The null standard deviation is estimated from the log density \citep{efron2004large}. For values of $z$ at and around the mode
\begin{equation}
  \ln p_{Z}(z) = 
  \ln\left[
    \dfrac{\pi_0}{\sqrt{2\pi}{\sigma}_0}
  \right]
  -\dfrac{1}{2}
  \left(
    \dfrac{z-{\mu}_0}{{\sigma}_0}
  \right)^2
  \ .
\end{equation}
Taking derivatives
\begin{align}
  \dfrac{\partial}{\partial z} \ln p_{Z}(z) &=
  -\left(
    \dfrac{
      z-{\mu}_0
    }
    {
      {\sigma}_0^2
    }
  \right)
  \\
  \dfrac{\partial^2}{\partial z^2} \ln p_{Z}(z) &=
  -\dfrac{
    1
  }
  {
    {\sigma}_0^2
  }
\end{align}
which motivates the estimator \citep{efron2004large}
\begin{equation}
  \widehat{\sigma}_0 = \left[
    \left.
      -\dfrac{\partial^2}{\partial z^2}\ln\widehat{p}(z)
    \right|_{z=\widehat{\mu}_0}
  \right]^{-1/2}
  \ .
  \label{eq:inference_nullStdEstimator}
\end{equation}
The evaluation of $z=\widehat{\mu}_0$ is used because at the mode, it was assumed that the null test statistics would dominate and non-null test statistics would not contribute much to the density estimate.

This method does not need estimations of $\pi_0$ which makes it quite convenient. Estimations of $\pi_0$ are discussed in literature such as \cite{benjamini2000adaptive, pounds2003estimating, storey2003statistical, pounds2004improving, langaas2005estimating, durnez2014posthoc}. \cite{efron2004large} motivated the use of the empirical null by investigating various types of false discovery rates \citep{storey2002direct, storey2003positive, efron2002empirical, efron2007size} which will not be discussed here.

The empirical null is used widely, including in neuroimaging \citep{schwartzman2008false, schwartzman2009empirical} and has been extended to include non-Normal null distributions \citep{schwartzman2008false, schwartzman2008empirical}. There exist various methods for the empicial null, for example, \cite{schwartzman2008empirical} used Poisson regression on the histogram counts in regions where the null statistics dominate. The empirical characteristic function was used in \cite{jin2007estimating}.

@@

The null mean was estimated by numerically finding the mode of the density estimate. The null standard deviation was estimated using Equation \eqref{eq:inference_nullStdEstimator}. This resulted in the empirical null density to have the same curvature as the density estimate at the mode, this is illustrated in Figure \ref{fig:inference_inferenceSubsample1_densityEstimate}. In this particular example, it was found that $\widehat{\mu}_0=\input{../figures/inference/inferenceSubsample1_nullMean.txt}$ and $\widehat{\sigma}_0=\input{../figures/inference/inferenceSubsample1_nullStd.txt}$ to 2 decimal places.

@@

The mode was found by solving $\widehat{\mu}_0 = \argmax\widehat{p}_Z(z)$ numerically. This was done by using the Newton-Raphson method to solve

@@

  \right) $,
so the log density is

@@

Taking the first-order derivative
